Max N and S

### 2019-10-29 analysis/reports/statevars.Rmd
setting up for hpg

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache.sqlite"))
cache <- storr::storr_dbi("datatable", "keystable", db)

>>>>

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-dat.sqlite"))
cache <- storr::storr_dbi("datatable", "keystable", db)
